\vspace{-2em}The 4th Workshop on Sustainable Software for Science: Best Practices and Experiences (WSSSPE4)

### 2016-06-10 WSSSPE4_proposal/WSSSPE4_proposal.tex
added 'for Science' to title...
added more to BI section in proposal
added section on assessment; may need more

\title{\vspace{-2em}The 4th Workshop on Sustainable Software: Best Practices and Experiences (WSSSPE4)
}
\author{Daniel S.\ Katz, University of Illinois Urbana--Champaign \\
        Gabrielle Allen, University of Illinois Urbana--Champaign \\
	Kyle E.\ Niemeyer, Oregon State University
	}
\date{}                                           % Activate to display a given date or no date

@@

\begin{shortlist}
\item Panel on best practices
\item Summary and discussion of each tracks’ progress
\item Planning for future events
\end{shortlist}

@@

@@

This proposal is focused primarily on encouraging diverse participation at the workshop, particularly from underrepresented groups and early stage researchers. Funds will be used to help facilitate a diverse set of participants, including panel and keynote speakers.

>>>>

\title{\vspace{-2em}The 4th Workshop on Sustainable Software for Science: Best Practices and Experiences (WSSSPE4)
}
\author{Daniel S.\ Katz, University of Illinois Urbana--Champaign \\
        Gabrielle Allen, University of Illinois Urbana--Champaign \\
	Kyle E.\ Niemeyer, Oregon State University
	}
\date{}                                           % Activate to display a given date or no date

@@

\begin{shortlist}
\item Panel on best practices
\item Summary and discussion of each tracks' progress
\item Planning for future events
\end{shortlist}

@@

\section{Assessment}

Reports describing the activities of WSSSPE and WSSSPE2 culminated in peer-reviewed articles~\cite{WSSSPE1,WSSSPE2}, while the report from WSSSPE3 is currently undergoing peer review (and is available via the arXiv)~\cite{WSSSPE3}; all reports are publicly available via publication in an open-access journal.
A similar report will be prepared at the conclusion of WSSSPE4, and following the practices of past workshops will be written collaboratively and openly on GitHub.

The organizers of WSSSPE4 take seriously the assessment of workshop activities, in particular the progress of each working group where applicable.
A portion of the first day's session is planned to discuss and evaluate the status\slash success of the activities proposed during WSSSPE3~\cite{WSSSPE3}.

@@

This proposal is focused primarily on encouraging diverse participation at the workshop, particularly from underrepresented groups and early stage researchers. Funds will be used to help facilitate a diverse set of participants, including panel and keynote speakers. 
Strategies for reaching\slash recruiting such participants will be solicited from members of the Program Committee with experience supporting students, researchers, and research software engineers with such backgrounds.
